\section{Future Work}

This research was one of the few recent efforts in the domain of
text-input mechanisms with backside touch input. There are many
directions that can serve as follow up to this work. Our
post-session/post-test interviews helped us in that regard.

Since the the speed of the chording mechanism seems to be limited by
its novelty, one important question is ``How can we quickly train
users to use the new mechanism, and maximize their engagement in the
learning process?''  As with other novel input mechanisms, if it is
too difficult for users to learn, they will not use it, even if it
performs much better ( for example, stenographer's text entry
systems).

Future research could also explore haptics and tactile feedback. This
would entail producing vibrations and other cues to signal a change on
the interface. Especially in the case of the chording mechanism,
whenever the user switches from one zone to the other, or selects a
new segment, it could be coupled with some feedback. This would also
help the interface to be used by visually challenged people as well.

The time that the users spent on the mechanisms was limited and short. They had to get accustomed to the interface in 20 minutes and then start on the test. Future research could be devoted to studying the effects of training times on KSPC and WPM. 

To further minimize the amount of movement in the chording mechanism,
future iterations of the mechanism should use the first touch to
select the zone, and the rest of the touches should select the segment
of the zone, irrespective of position. Therefore, the user won't be
required to try and bring all their fingers into a particular
zone. Instead they would just take one finger to a particular zone and
then place the others at any random location thereby selecting the
segments in the zone that was selected by the first finger. This would
considerably reduce the effort involved in the chording mechanism, and
would also make the interface even less sensitive to positioning.

In the introduction we talked about how there were some scenarios that
we envisioned and observed. However, since this was an exploratory
study we wanted to control as many variables as possible. Therefore,
very similar conditions were reproduced for all the
participants. Future work should test the applications in various
different scenarios, and analyze the appropriateness of different
mechanisms in different scenarios.
