\documentclass{chi2011}
\usepackage{times}
% \usepackage{url}
\usepackage{graphics}
\usepackage{color}
\usepackage[pdftex]{hyperref}
\hypersetup{%
pdftitle={Your Title},
pdfauthor={Your Authors},
pdfkeywords={your keywords},
bookmarksnumbered,
pdfstartview={FitH},
colorlinks,
citecolor=black,
filecolor=black,
linkcolor=black,
urlcolor=black,
breaklinks=true,
}
\newcommand{\comment}[1]{}
\definecolor{Orange}{rgb}{1,0.5,0}
\definecolor{grey}{rgb}{0.6,0.6,0.6}
\newcommand{\todo}[1]{\textsf{\textbf{\textcolor{Orange}{[[#1]]}}}}

\pagenumbering{arabic}  % Arabic page numbers for submission.  Remove this line to eliminate page numbers for the camera ready copy

\begin{document}
% To make various LaTeX processors do the right thing with page size.
\special{papersize=8.5in,11in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}

% Use this command to override the default ACM copyright statement
% (e.g. for preprints). Remove for camera ready copy.
\toappear{Submitted for review to CHI 2011.}

\title{Text input mechanisms for devices with backside touch input}
\numberofauthors{2}
\author{
  \alignauthor Author 1\\
    \affaddr{Affiliation}\\
    \affaddr{Affiliation}\\
    \email{author@a.com}
  \alignauthor Author 2\\
    \affaddr{Affiliation}\\
    \affaddr{Affiliation}\\
    \email{author2@b.com}
}

\maketitle

\begin{abstract}
 Text input on medium-sized is problematic because of added weight, increased finger movement, and lack of tactile feedback. Such devices are used in various different scenarios. Due to the increased interest in devices with backside touch input, avenues for investigation of alternate text input mechanisms have increased manifold. In this paper we present the design, development and user testing of three text input mechanisms on a device with backside touch input. The three mechanisms, namely QWERTY, backside QWERTY and chording were tested in a controlled environment. In addition to quantitative results on speed and accuracy of the mechanisms, we also present the quantitative analysis of our qualitative findings obtained through the NASA-TLX experiment.
\end{abstract}

\keywords{QWERTY, multitouch, touchscreens, keystroke per character(KSPC), words per minute(WPM)} 

\category{H.5.2}{Interaction techniques and devices}{Touchscreens, Text input}


\input{tex/Introduction.tex}

\input{tex/Related.tex}

%\input{tex/Scenarios.tex}

\input{tex/Experiments.tex}

\input{tex/System.tex}

\input{tex/Mechanisms.tex}


\input{tex/Results.tex}


\input{tex/Future.tex}

\input{tex/Conclusion.tex}

\bibliographystyle{abbrv}
\begin{thebibliography}{1}
\bibitem{1} Adam PC http://notionink.wordpress.com
\bibitem{2} BlinType http://www.blindtype.com
\bibitem{3} SWYPE http://www.swypeinc.com
\bibitem{4} Ekatetra http://www.ekatetra.com
\bibitem{5} Twiddler http://www.handykey.com
\bibitem{6} http://sloan.stanford.edu/mousesite/1968Demo.html
\bibitem{7} Gopher, D., and Raij, D. (1988) "Typing with a two hand chord keyboard - will the QWERTY become obsolete?" IEEE Transactions in System Man and Cybernetics 18, 60l-609. 
\bibitem{8} Shin, H., Lee, W., Lee, G., and Cho, I. 2009. Multi-point touch input method for Korean text entry. In Proceedings of the 27th international Conference Extended Abstracts on Human Factors in Computing Systems (Boston, MA, USA, April 04 - 09, 2009). CHI '09. ACM, New York, NY, 3871-3876.
\bibitem{9} Schmidt T., Konig W., Reiterer H. Text Input on Multitouch Tabletop Displays. EuroVis 2009.
\bibitem{10} Brewster, S.A., Lumsden, J., Bell, M., Hall, M. and Tasker, S. Multimodal 'Eyes-Free' Interaction Techniques for Wear-able Devices. In Proceedings of ACM CHI 2003, ACM Press, Addison-Wesley, 463-480.
\bibitem{11} Cechanowicz, J., Irani, P. and Subramanian, S. Augmenting the Mouse with Pressure Sensitive Input. In Proceedings of ACM CHI 2007, ACM Press, Addison Wesley, 1385-1394.
\bibitem{12} Hoggan, E., Brewster, S.A. and Johnston, J. Investigating the Effectiveness of Tactile Feedback for Mobile Touchscreens. In Proceedings of ACM CHI2008, ACM Press Addison Wesley, 1573-1582.
\bibitem{13} Holleis, P., Huhtala, J. and Häkkilä, J. Studying applications for touch-enabled mobile phone keypads. In Proceedings of TEI 2008, ACM Press,15-18.
\bibitem{14} Mackenzie, I.S., Zhang, S. and Soukoreff, R.W. Text Entry Using Soft Keyboards. Behaviour and Information Technol-ogy, 1999, 18 (4), 235 - 244.
\bibitem{15} Ramos, G., Boulos, M. and Balakrishnan, R. Pressure Wid-gets. In Proceedings of ACM CHI 2004, ACM Press, Addi-son-Wesley, 487-494.
\bibitem{16} Sears, A., Revis, D., Swatski, J., Crittenden, R. and Shnei-derman, B. Investigating Touchscreen Typing: The Effect of Keyboard Size on Typing Speed. Behaviour and Information Technology, 1993.
\bibitem{17} www.yorku.ca/mack/phrases2.txt
\bibitem{18} Hart, S., and Staveland, L. (1988). Development of NASA-TLX (Task Load Index): Results of empirical and theoretical research. In P. Hancock and N. Meshkati (Eds.), Human mental workload (pp. 139-183). Amsterdam: North Holland.
\bibitem{19} Hart, S. (2006). Nasa-Task Load Index (Nasa-TLX); 20 Years Later. Human Factors and Ergonomics Society Annual Meeting Proceedings, 50, 904-908.
\bibitem{20}
\end{thebibliography}

\end{document}