\section{Scenarios}

We envisioned some scenarios where people might need alternative text
input mechanisms. For each scenario, we then proposed a possible
mechanism that could be helpful in entering text with accuracy, and
reasonable speed. It should be noted that the theme of research was
not to necessarily outrun soft QWERTY in terms of speed, but to
propose mechanisms that could work with reasonable performance in
scenarios listed.

\subsection{Stationary and visually focused}

This is the best case scenario, and also the one that soft-QWERTY
keyboard is perfectly suited for. In this scenario, the user is
stationary (not walking or moving) and can adjust to reach an optimal
configuration. This includes resting the device on the lap, and
entering text similar to an actual keyboard.

\subsection{Mobile and visually focused}

This is the case where the user is moving but has enough time to do
operations that require visual focus on the screen. This includes
scenarios like commuting (standing or sitting). The challenge here is
that due to occasional loss of focus while entering the text, users
have to orient themselves again after each lapse. Such scenarios would
require mechanisms that don't necessarily require the used to
re-orient themselves time and again. In short, mechanisms designed for
such scenarios would allow the user to constantly touch the screen and
still be able to signal input, as and when required.

\subsection{Mobile and intermittently focused}

This is the worst case scenario, and it occurs in cases when the user
is otherwise involved in some activity, but still has a need to enter
text. This includes walking, when the user is actually focused on the
path and is entering text on the side. Being able to enter text in
this scenario, on devices of larger form factor is a challenge. Such
scenarios would require mechanisms that have unique formations or
representations that the user can memorize over time. This also means
that the mechanisms would reduce the amount of visual search that the
user has to perform, in order to enter a particular character.
 
